---
title: "Hello R"
author: "Gaspar Sanchez"
date: "Data 2401"
output: 
  html_document: 
    fig_width: 14
    fig_height: 14
---

MAKE SURE YOU READ AND FOLLOW **ALL** INSTRUCTIONS ON THE INSTRUCTION DOCUMENT. 

### Load packages

```{r load-packages, message=FALSE}
library(tidyverse) 
library(datasauRus)
```


### Exercise 1
There are a total of 3 columns and 1846 rows and the variables are Dataset, x and y

### Exercise 2

First let's plot the data in the dino dataset:

```{r plot-dino, fig.height=3, fig.width=6}
dino_data <- datasaurus_dozen %>%
  filter(dataset == "dino")
ggplot(data = dino_data, mapping = aes(x = x, y = y)) +
  geom_point()
```

And next calculate the correlation between `x` and `y` in this dataset:

```{r cor-dino}
dino_data %>%
  summarize(r = cor(x, y))
## # A tibble: 1 x 1
## r
## <dbl>
## 1 -0.0645
```

### Exercise 3

Star Plotting



```{r plot-star}
plot_star <- datasaurus_dozen %>%
  filter(dataset == "star")
ggplot(data = plot_star, mapping = aes(x = x, y = y)) +
  geom_point()

```

And next calculate the correlation between `x` and `y` in this dataset:
 
```{r cor-star}
plot_star %>%
  summarize(r = cor(x, y))

```

### Exercise 4

Plot for Circle

```{r plot-circle}
plot_circle <- datasaurus_dozen %>%
  filter(dataset == "circle")
ggplot(data = plot_circle, mapping = aes(x = x, y = y)) +
  geom_point()

```
And next calculate the correlation between `x` and `y` in this dataset:
```{r cor-circle}
plot_circle %>%
  summarize(r = cor(x, y))

```
### Exercise 5
All of the Plots at once
```{r datasaurus_dozen}
ggplot(datasaurus_dozen, aes(x = x, y = y, color = dataset))+
geom_point()+
facet_wrap(~ dataset, ncol = 3) + # facet the dataset variable, in 3 cols
theme(legend.position = "none")
```
All correlations of x and y
```{r cor-datasaurus_dozen}
datasaurus_dozen %>%
group_by(dataset) %>%
summarize(r = cor(x, y)) %>%
print(13)
```






